Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-26 paper/paper.tex
#30 finish review of v0.9(.1)
#29 commit before big changes
#29 clarify exposition of results

Table \ref{tab:baseline_50y} shows estimates from Equation \eqref{eq:baseline}. This is a difference-in-differences specification with added interactions to capture heterogeneous treatment effects. As before, different columns use different subsets of construction as the outcome variable.

I report estimates of the coefficient of interest $\theta_{conquest}$ in the second row. In Column (1) we can see that the probability of construction activity in a given period is 4 percentage points higher following a conquest vis-a-vis after a succession, but the difference is not statistically significant.

The only subset of construction that shows a significant effect is state construction --- palaces, castles, military and administrative buildings. We can see in Column (2) that these are 5 percentage points \textit{less} likely to be built in a city after it was conquered; the effect is significant at the 5\% level.

The hypothesis was that conflict-driven selection for state power boosts urban growth. Given that my assumption about the difference in selectivity of conquests and successions holds true, the theory would have predicted a positive coefficient $\theta_{conquest}$. The results I obtain instead range from insignificant to negative. They offer no support to the hypothesis.

@@

I test the robustness of this result by estimating some alternative specifications. Table \ref{tab:controls_50y} shows estimates of Equation \eqref{eq:baseline} obtained with different sets of control variables. The outcome is $All \, construction$ in all regressions. Column (1) is identical to Column (1) in Table \ref{tab:baseline_50y} and controls only for switching in the same period. In Column (2) I remove this control. Columns (3) and (4) add conflict as a control variable, once in addition to switching and once without.

>>>>

Table \ref{tab:baseline_50y} shows estimates from Equation \eqref{eq:baseline}. This is a difference-in-differences specification with added interactions to capture heterogeneous treatment effects. As before, different columns use different subsets of construction as the outcome variable. Since successions are omitted from the interaction terms, the coefficient $\pi$ on the post-treatment dummy $Switch\,to\,another\,state$ captures the treatment effect of switching states via succession. The interaction terms are relative to that: the coefficient $\theta_{conquest}$ on $Switch\,to\,another\,state \times Conquest$ is the difference between the treatment effect of switching via succession, and the treatment effect of switching via conquest.

In Column (1) we can see that the probability of construction activity in a given period is 4 percentage points higher following a conquest vis-a-vis following a succession. The treatment effect of a conquest (compared to no treatment) is $0.02 + 0.04 = 0.06$, while the treatment effect of a succession is $0.02$. Crucially, though, the difference between them is not statistically significant.

The only subset of construction for which the difference in trends is significant is state construction --- palaces, castles, military and administrative buildings. We can see in Column (2) that these are 5 percentage points \textit{less} likely to be built in a city after it was conquered; the effect is significant at the 5\% level. BLANK.

The hypothesis was that conflict-driven selection for state power boosts urban growth. Given that my assumption about the difference in selectivity of conquests and successions holds true, the theory would have predicted a positive coefficient $\theta_{conquest}$. The estimates I obtain instead range from insignificant to negative. They offer no support to the hypothesis.

@@

I test the robustness of this second result by estimating Equation \eqref{eq:baseline} with different control variables $\textbf{X}_{it}$. We can see in Table \ref{tab:controls_50y} shows estimates of  obtained with different sets of control variables. The outcome is $All \, construction$ in all regressions. Column (1) is identical to Column (1) in Table \ref{tab:baseline_50y} and controls only for switching in the same period. In Column (2) I remove this control. Columns (3) and (4) add conflict as a control variable, once in addition to switching and once without.
